LAGOS lake depth

### 2020-06-23 figures/01_geometry.Rmd
rm white background in spacers and legend

```{r 01_geometry_grid, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=5.5, fig.height=4.2}
theme_opts <- cowplot::theme_cowplot() + 
  theme(legend.position = "none", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 11))
gg_spacer <- ggplot() + geom_blank() + theme(panel.background = element_blank())

legend_shape     <- cowplot::get_legend(gg_scatter_shape +
                                          theme(legend.direction = "horizontal"))
legend_reservoir <- cowplot::get_legend(gg_scatter_reservoir + labs(color = "") +
                                          theme(legend.direction = "horizontal"))
legend_panel     <- cowplot::plot_grid(gg_spacer, legend_shape, 
                                       gg_spacer, legend_reservoir, 
                                       nrow = 1, rel_widths = c(0.2, 1, 0.08, 1),
                                       align = "hv")

>>>>

```{r 01_geometry_grid, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=5.5, fig.height=4.2}
theme_opts <- cowplot::theme_cowplot() + 
  theme(legend.position = "none", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 11))
gg_spacer <- ggplot() + geom_blank() + theme(panel.background = element_rect(fill = NA), plot.background = element_rect(fill = NA))

legend_shape     <- cowplot::get_legend(gg_scatter_shape +
                                          theme(legend.direction = "horizontal", legend.background = element_rect(fill = NA)))
legend_reservoir <- cowplot::get_legend(gg_scatter_reservoir + labs(color = "") +
                                          theme(legend.direction = "horizontal", legend.background = element_rect(fill = NA)))
legend_panel     <- cowplot::plot_grid(gg_spacer, legend_shape, 
                                       gg_spacer, legend_reservoir, 
                                       nrow = 1, rel_widths = c(0.2, 1, 0.08, 1),
                                       align = "hv")
